### 2024-07-24 modern-portfolio-theory.qmd
Built site for gh-pages

@@

@@

>>>>

## Fantasy Football is Like Stock Picking

@@

Okay, fantasy football might be similar to stock picking, so what?
You are most likely to pick the best players if you go with the wisdom of the crowd (e.g., average projections) and diversify.
Most projections are public information, so you might wonder whether using crowd projections gains you anything because everybody else has access to public information.
However, this is also the case with stocks, and people still consistently perform best over time when they go with the market.

@@

## The Efficient Frontier

The ultimate goal is to draft players for your starting lineup that provide the most projected points and the smallest downside risk.
This is similar to the notion in investing of the efficient frontier, where your goal is to pick funds that have the greatest expected returns for the least risk (where risk is the variability in returns over time).
